\documentclass{arabicClass}

\begin{document}
	
	\renewcommand{\theequation}{\arabic{equation}.\arabic{chapter}}
	
	\renewcommand{\arraystretch}{1.3}
	
	\abovedisplayskip=7pt
	\belowdisplayskip=7pt
	
	\input{Title Page/titlepage}
	\pagenumbering{roman}
	\input{ayah}
	\input{gift}
	\input{thanks}
		\tableofcontents
		\clearpage
		\pagenumbering{arabic}
	\input{abstract}
	\input{intro}

	\input{chapter1}
	\input{chapter2}
	\input{chapter3}
	
	\input{conclusion}
	

	
\begin{thebibliography}{99}
	\addcontentsline{toc}{chapter*}{المصادر}	
	\begin{english}
		\bibitem{Bellman} 
		Bellman RE, Kashef BG, Casti J, \textit{Differential quadrature: a technique for the rapid solution of non-linear partial differential equations}, J Comput Phys, Vol 10, pp 40-52, 1972.
		
		\bibitem{bellman_roth} 
		Bellman RE, Roth RS, \textit{Methods in approximation: techniques for mathematical modelling}, D Reidel Publishing Company, Dordrecht, Holland, 1986.
		
		\bibitem{bert} 
		Bert CW, Malik M, \textit{Differential quadrature: a powerful new technique for analysis of composite structures}, Compos. Struct., Vol 39, Iss 3-4, pp 179-189, 1997.
		
		\bibitem{chang_shu} 
		Chang Shu, \textit{Differential Quadrature and its Applications in Engineering}, Springer-Verlag London, 1999.
		
		\bibitem{chang_tsai} 
		Chang CT, Tsai CS, Lin TT, \textit{The modified differential quadratures and their applications}, Chem. Eng. Comman., Vol 123, pp 135-164, 1993.
		
		\bibitem{finite_volume} 
		LeVeque RJ, \textit{Finite Volume Methods for Hyperbolic Problems}, Cambridge University Press, Vol 31, pp 1-20, 2002.
		
		\bibitem{navier_stokes} 
		Girault V and Raviart PA, \textit{Finite Element Methods for Navier-Stokes Equations: Theory and Algorithms}, Springer Series in Computational Mathematics, Vol 1, pp 1-100, 1986.
		
		\bibitem{Quan} 
		Quan JR, Chang CT, \textit{New insights in solving distributed system of equations by the quadrature methods}, Comput. Chem. Engrg., Vol 13, pp 779-788, 1989.
		
		\bibitem{finite_difference} 
		Smith GD, \textit{Numerical Solution of Partial Differential Equations: finite difference methods}, Oxford University Press, 1985.
		\end{english}
\end{thebibliography}


	\input{entitlepage}

\end{document}